---
title: "Week 3 Assignment"
author: "LeTicia Cancel"
date: "9/10/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1

Code that identifies majors that contain either "DATA" or "STATISTICS" from [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/](Five Thirty Eight)

```{r}
library(rvest)

site <- "https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/"

majors_list <- read_html(site)

# pull all majors
majors_list %>%
  html_nodes(xpath = '//*[@id="example"]/tbody/tr[1]/td[1]') %>%
  as.character()

html_table(major_section)
```

## Question 2

Data transformation

## Question 3

Describe, in words, what these expressions will match:

* (.)\1\1

* "(.)(.)\\2\\1"

* (..)\1

* "(.).\\1.\\1"

* "(.)(.)(.).*\\3\\2\\1"


## Question 4

Construct regular expressions to match words that:

Start and end with the same character.
```{r}

```

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}

```

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r}

```

