---
title: "Week 3 Assignment"
author: "LeTicia Cancel"
date: "9/10/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1

Code that identifies majors that contain either "DATA" or "STATISTICS" from [Five Thirty Eight] (https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/). 

```{r warning=FALSE, message=FALSE}
library(rvest)
library(xml2)
library(tidyverse)

# Get URL of College Majors list
site <- "https://projects.fivethirtyeight.com/mid-levels/college-majors/index.html?v=3"
majors_list <- read_html(site)

# Scrape all data from the website
majors_df <- majors_list %>%
  html_nodes(xpath = '//*[@id="example"]') %>%
  html_table(fill = TRUE)

# Scrapped data is in the form of a list. 
# Convert list to data frame and save the majors column only to its own data frame
majors_df <- as.data.frame(majors_df)
mj <- majors_df$MAJOR

# look for majors with statistics in name
major.stats <- str_view(mj, regex("statistics", ignore_case = TRUE), match = TRUE)

# look for majors with data in the name
major.data <- str_view(mj, regex("data", ignore_case = TRUE), match = TRUE)

# Display all majors with Statistics in the name
major.stats

# Display all majors with Data in the name
major.data
```

## Question 2

Data transformation

```{r message=FALSE, warning=FALSE}
library(RCurl)
library(dplyr)

# get fruit list from Github
x <- getURL("https://raw.githubusercontent.com/ltcancel/Homework3_Data607_F20/master/fruit.txt")
fruit <- read.delim(text = x, header = FALSE, sep = '"')

fruit

```

```{r}
# filter to only include columns with values
fruit.clean <- fruit %>%
  select(2,4,6,8)

fruit.clean

```

```{r}
# loop through data frame to create final string

for (x in 1:nrow(fruit.clean)){
  for (y in 1:ncol(fruit.clean)){
    if (x == 1 && y == 1){
      final.string <- c("c(",fruit.clean[x,y])
    }
    else if (x == nrow(fruit.clean) && y == ncol(fruit.clean)){
      final.string <- paste0(final.string,")")
    }
    else{
      final.string <- paste0(final.string,",",fruit.clean[x,y])
    }
  }
}

# Display new string
final.string
```

## Question 3

Describe, in words, what these expressions will match:

* (.)\1\1
  + This will find the same letter repeating 3 times in a row. Example: bbb


* "(.)(.)\\2\\1"
  + This will find 2 letters grouped, then find the same letters grouped in reverse. Example: chhc
  

* (..)\1
  + This will find 2 letters that repeat once. Example: Chch
  

* "(.).\\1.\\1"
  +  This will find 1 letter that repeats 3 times but is not grouped together. Example: exexe
  
* "(.)(.)(.).*\\3\\2\\1"
  + This will find 3 letters grouped, followed by any character, and then find the same 3 letter but grouped in reverse. Example: xyz1zyx


## Question 4

Construct regular expressions to match words that:

Start and end with the same character.
```{r}
str_view(c("dad","apple","eye"),"^(.).*\\1$")
```

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}
str_view(c("church","house","pressure"),"(..).*\\1", match = TRUE)
```

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r}
str_view(c("eleven","six","between"),"(.).*\\1.*\\1")
```

