---
title: "Week 3 Assignment"
author: "LeTicia Cancel"
date: "9/10/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1

Code that identifies majors that contain either "DATA" or "STATISTICS" from [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/](Five Thirty Eight). 

```{r}
#install.packages("xml2")
library(rvest)
library(xml2)
library(tidyverse)
library(stringr)

site <- "https://projects.fivethirtyeight.com/mid-levels/college-majors/index.html?v=3"

majors_list <- read_html(site)

# pull all majors
majors_df <- majors_list %>%
  html_nodes(xpath = '//*[@id="example"]') %>%
  html_table(fill = TRUE)

#convert list to data frame and save majors column only to its own data fram
majors_df <- as.data.frame(majors_df)
mj <- majors_df$MAJOR

#look for majors with statistics in name
str_view(mj, regex("statistics", ignore_case = TRUE), match = TRUE)

#look for majors with data in the name
str_view(mj, regex("data", ignore_case = TRUE), match = TRUE)

```

## Question 2

Data transformation

## Question 3

Describe, in words, what these expressions will match:

* (.)\1\1

* "(.)(.)\\2\\1"

* (..)\1

* "(.).\\1.\\1"

* "(.)(.)(.).*\\3\\2\\1"


## Question 4

Construct regular expressions to match words that:

Start and end with the same character.
```{r}

```

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}

```

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r}

```

